Chatbots in the classroom: an analysis from the teacher's perspective

### 2021-05-21 edubots_surveys.Rnw
Does update new ones in pdf for RQ1 refs #13
Fixes image sizes, automatically generated now
Extends RQ1 discussion with messaging organization data refs #13

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_provided.eps}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_provided.eps}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_provided.eps}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_whatsapp.eps}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_whatsapp.eps}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_whatsapp.eps}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_telegram.eps}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_telegram.eps}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_telegram.eps}
    \end{minipage}
\end{center}
    \caption{Use of chatbots in class: distributions per gender and age. Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
\label{figure:chatbots_use_gender_age_exp}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_provided.eps}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_provided.eps}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.eps}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.eps}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_telegram.eps}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.eps}
    \end{minipage}
\end{center}
    \caption{Differences in the use of chatbots in class between vocational and university teaching and distributions by discipline.}
\label{figure:chatbots_use_sector_discip}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.45\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.45\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.45\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
    \end{minipage}
\end{center}
    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
\label{figure:chatbots_use_postcovid}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
    \end{minipage}
\end{center}
    \caption{Use of chatbots in class: distributions per gender and age. Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
\label{figure:chatbots_use_gender_age_exp}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
    \end{minipage}
\end{center}
    \caption{Differences in the use of chatbots in class between vocational and university teaching and distributions by discipline.}
\label{figure:chatbots_use_sector_discip}
\end{figure}

Regarding the social factor of chat groups that teachers use in class, according to Fig. \ref{figure:chatbots_messagingorganization} the vast majority prefer small groups only with the students from the same course. These are more focused groups with specific goals and dedicated to the organization of the course and its tasks, and from the pedagogic point of view seem more appropriate to improve the learning process. Interestingly, about 30\% of teachers consider they should not be part of the chat group. Also, only university teachers find interesting a group with all the students and teachers in their own Faculty or School. The lack of teachers from vocational Education here may be the consequence of using specific language such as "Faculty". Moreover, the fact that many universities and schools already use these groups for administrative and social interaction (e.g. \cite{dibitonto2018chatbot}) might be the reason for the low percentage of teachers that selected this response.

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
\caption{XXX}
\label{figure:chatbots_messagingorganization}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
    \end{minipage}
\end{center}
    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
\label{figure:chatbots_use_postcovid}
\end{figure}
